% LaTeX resume using res.cls
\documentclass[overlapped]{res}
\usepackage{parcolumns}
\usepackage{hyperref}
\usepackage{enumitem}
\setlength{\textwidth}{7.5in} % set width of text portion
\addtolength{\oddsidemargin}{-0.95in}
% \addtolength{\oddsidemargin}{-0.85in}
\addtolength{\topmargin}{-0.95in}
\addtolength{\textheight}{1.75in}
\addtolength{\sectionwidth}{-0.2in}
\addtolength{\sectionskip}{-0.1in}



\begin{document}
\begin{resume}


% Center the name over the entire width of resume:
\centerline{\Large\bf Cody Morterud}
% Draw a horizontal line the whole width of resume:
\vbox{\hrule width 1\textwidth height 1pt}\smallskip
% address begins here
% Again, the address lines must be centered over entire width of resume:
\centerline{ 
    codymorterud@gmail.com 
    $\cdot$ \href{http://www.codymorterud.com}{www.codymorterud.com} $\cdot$ (248) 481-0355
    $\cdot$ South Lyon, MI
}

\section{EDUCATION} 
\textbf{University of Michigan, Ann Arbor, MI}
\hfill April 2019\\ 
                 {\sl Bachelor of Science in Engineering,} Computer Science,
                 {\sl With Honors, Magna Cum Laude}\hfill 3.50/4.00 GPA\\
                % \\ {\sl Minor in Mathematics}
\textbf{Georgia Institute of Technology, Atlanta, GA}
\hfill May 2023\\ 
                 {\sl Master of Science,} Computer Science, {\sl Computing Systems} \hfill 4.00/4.00 GPA
                % \\ {\sl Minor in Mathematics}

\section{EXPERIENCE}
\textbf{Capital One, Chicago, IL}  \\
{\sl Senior Associate Software Engineer} \hfill February 2021 - Current \\
{\sl Associate Software Engineer} \hfill August 2019 - February 2021
\begin{itemize}  \itemsep -2pt % reduce space between items
    \item Complete responsibility for multiple ECS Java Spring Boot business critical REST API microservices in AWS.
    \item Moderate Java Spring Boot microservice feature contributions to ensure clean code and object oriented principles.  %ensuring production stability and timely feature delivery. %to ensure production stability and feature delivery on-time.
    \item Validate and conduct production releases in AWS for stakeholders independently and safely with no downtime.
    \item Guide technical debt reduction intent through continuous identification and scrum story creation.
    % \item Increased developer productivity by advocating for and rewriting an EC2 based application to AWS Lambda.
    \item Promoted CICD practices by investing time and efforts into expanded testing as part of pipelines.
    \item Conduct production support and contribute hotfixes when necessary.
    \item Inner sourced microservice platform, insituting code quality standards, documentation, and requirements for features.
    \item Planned, documented, performed, and validated critical production traffic failover for technical recovery exercise. 
    \item Decreased service latency 20\% by multithreading external
    API calls and validated changes with performance testing.
    \item Promoted software engineering practices by presenting and teaching common design patterns within the ART. 
    \item Ensured production deployment validation by designing 
    and implementing acceptance tests with Cucumber.
    \item Deployed applications to AWS by
    writing and programmatically configuring build stages within {\it Jenkinsfile}s.
    % \item Wrote documentation for services owned by team to onboard feature teams to our applications.
    \item Advocated, presented, and implemented application design improvements to department scrum meetings.
    % \item Designed and installed roles of least privilege in PostgreSQL databases.
    \item Removed attack vectors via consistent dependency updates, cybersecurity vulnerability scanning, and testing.
    % \item Designed comprehensive suites of custom alerts through Kibana
    % for production incidents for multiple services.
\end{itemize}

\textbf{Quicken Loans, Detroit, MI} \\
{\sl Software Developer Intern}  \hfill May 2018 - August 2018
\begin{itemize}  \itemsep -2pt %reduce space between items

    \item Addressed internal research for a new internal intern networking service
    and won hackathon award
    by implementing, presenting, and demoing 
    a brand new cloud-based internal
    networking platform with a team of interns via
    AWS Lambda, DynamoDB, API Gateway, S3 and Cloudfront.

    \item Automated InRule test suites by developing, testing, and publishing 
    C\texttt{\#} .NET Nuget package to add
    necessary functionality to InRule testing environment.

    \item Promoted continuous integration standards by setting up build templates to build,
    test, apply secrets, conduct code analysis,
    and check quality gates before release.

    % \item Met continuous deployment quality gates by writing unit tests
    % with NUnit and MOQ to ensure high code coverage.

    % \item Standardized data models across services
    % and promoted best practices
    % by publishing Nuget class library package.

    % \item Provided visibility into DynamoDB for business users
    % by designing Splunk dashboard with use of
    % custom queries.

    % \item Identified bottlenecks in services by adding application-level
    % metrics logging to services via InfluxDB,
    % and set up Grafana dashboards to visually view the metrics.

    % \item Ensured service level agreements are met by setting up email alerting 
    % for production errors and high service latency.

    % \item Met business requirements for applications by learning
    % and developing in domain specific language.

    % \item Tracked and measured feature and story progress through
    % Agile framework ceremonies and scrums.

\end{itemize}

\textbf{The Boyle Lab, Ann Arbor, MI}\\
{\sl Research Assistant} \hfill October 2016 - May 2018
    \begin{itemize}  \itemsep -2pt %reduce space between items
    \item Decreased data processing time approximately 80\% 
    and increased research throughput
    by translating and refactoring statistical analysis program 
    from Perl to C\texttt{++}.
    
    \item Identified bottlenecks in algorithm by analyzing stack trace samples with \textit{perf}.
    
    % \item Satisfied design requirements by integrating third-party programs 
    % and libraries into project.
    
    % \item Maximized performance by using 
    % Standard Template Library containers and algorithms.
    % and tracked changes via version control systems.

    % \item Ensured accurate implementation and results by working closely
    %  with benefactors and stakeholders.
\end{itemize}

\section{PROJECTS}

\begin{itemize}[label={}]  \itemsep -2pt %reduce space between items
    \item \textbf{C\texttt{++}, Make, GDB:}
        Implemented, tested, debugged, and monitored multithreaded internet crawler
        for search engine build side to retrieve and save 3.5 million HTML documents
        at approximately 39,000 documents per hour on a 25 Mbps connection,
        prioritizing frontier of links, managing set of seen pages, parsing and caching Robots.txt files.
    \item \textbf{C\texttt{++}, CMake, Zookeeper, gRPC, Azure}
        Developed and tested scalable, parallel MapReduce framework implementation in C\texttt{++}
        serving jobs in Azure on infrastructure built with Azure Resource Manager templates.
    % \item \textbf{C, Make, GDB:}
    %     Developed virtual CPU and memory resource coordinator to manage
    %     virtual resources for guest operating systems running on top of a hypervisor,
    %     integrating with \textit{libvirt} APIs.
    % \item \textbf{C\texttt{++}, Make, GDB:}
    %     Developed MapReduce implementation to scalably perform MapReduce jobs in a multithreaded, distributed manner.
    \item \textbf{Python, Ryu Controller, Open vSwitch}
        Built virtualized network function manager to allow scaling of virtual network functions and 
        user defined routing between endhosts, handling arbitrary routing on a two switch topology.
    \item \textbf{C, Make, GDB:}
        Constructed several implementations of popular barrier synchronization
        algorithms in OpenMP and MPI; tested across separate nodes and threads to identify
        performance trends.
    % \item \textbf{C\texttt{\#} .NET, WPF:}
    %     Designed open source message encryption user interface using
    %     Windows Presentation Forms to allow non-technical users
    %     to encrypt and decrypt with AES-128 and AES-256 in CBC mode.
        % according to NIST standards
    % \item \textbf{Python, Flask, React, SQLite:}
    %     Implemented Instagram clone with basic functionality 
    %     to gain familiarity with the Flask and React frameworks, 
    %     developing web pages via templating, 
    %     and database construction with SQLite.
    % \item \textbf{Python:}
    %     Developed MapReduce master and worker server system 
    %     with REST API interface to serve concurrent MapReduce jobs
    %     and gain experience programming asynchronously.
    % \item \textbf{C\texttt{++}, Make, GDB:} Devised asynchronous, 
    %     network file system with user and request
    %     validation for CRUD operations to study file system implementation
    %     and socket programming.
    %  \item \textbf{C\texttt{++}, Make, GDB:}
    %      Implemented thread library 
    %      to gain experience with concurrent
    %      programming utilities such as threads, mutexes, and condition variables.
    %  \item \textbf{Python, PyTorch:}
    %      Classified photos of monuments into one of ten classes
    %      with a 6-layer convolutional neural network
    %      to learn practical application of neural networks on images with PyTorch.
    %\item \textbf{Python, MapReduce, Flask:}
    %Built Wikipedia search engine with use of Hadoop 
    %to construct an inverted index via MapReduce
    %to calculate cosine similarity scores 
    %to facilitate user search queries.
    % \item Developed single-level pager for a simulated system to efficiently
    % allocate virtual pages to memory
    % and reduce page faults and learn about memory management unit implementation.
\end{itemize}

\section{COMPUTER SKILLS}
\bigskip
\begin{parcolumns}[rulebetween,distance=2em,nofirstindent=true,colwidths={3=4.5cm}]{5}
    \colchunk[1]{\textbf{Languages}\\C/C\texttt{++}\\Python\\Java\\JavaScript\\\LaTeX}
    % \colchunk[2]{\textbf{IDE}\\IntelliJ\\Visual Studio\\VIM}
    \colchunk[2]{\textbf{Technologies}\\Git\\Bash\\Splunk\\Kibana\\Docker\\GDB}%\\Valgrind}
    \colchunk[3]{\textbf{Concepts}\\Multithreading\\Object Oriented Programming\\Linux Administration\\Networking Protocols\\Functional Testing\\Scrum}
    \colchunk[4]{\textbf{Java}\\Spring Boot\\Maven\\Mockito\\Mockserver\\Testcontainers}
    \colchunk[5]{\textbf{AWS CSAA}\\EC2\\ECS\\RDS\\ALB\\CloudWatch\\Lambda}
\end{parcolumns}

\end{resume}
\end{document}

